Supplementary Materials And Methods

### 2019-09-17 Supplementary_mat_met.Rmd
eval

```{r, fig.cap= "Percentage of affected nodes of each iteration for SERPINE2 Gene"}
as.data.frame(E9GE_mirnagenenormal)%>%
 priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
 update_how("SERPINE2",2.75) %>%
 simulate(150) %>%
 find_iteration(limit=1, plot= TRUE) #limit=1 describes the change that is not taken into account.
```

@@

```{r}
as.data.frame(E9GE_mirnagenenormal)%>%
 priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
 update_how("SERPINE2",2.75) %>%
 simulate(100) %>%
 find_iteration(limit=1, plot= FALSE)

@@

```{r}

@@

```{r}
as.data.frame(E9GE_mirnagenenormal)%>%
  priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
  update_how("SERPINE2",2.75)%>%
  simulate(62)%>%
  as_tibble()%>%
  select(name, initial_count, count_current)->simulation_results
```

### 2.5.3 Comparison of simulation results and tumor tissue expression values
```{r}
E9GE_mirnagenetumor%>%
  dplyr::select(hgnc_symbol, GE_tumor)%>%
  dplyr::inner_join((E9GE_mirnagenenormal%>%dplyr::select(hgnc_symbol, GE_normal)), by ="hgnc_symbol")%>%
  inner_join(simulation_results, by= c("hgnc_symbol"="name"))%>%
  distinct()
```

>>>>

```{r, fig.cap= "Percentage of affected nodes of each iteration for SERPINE2 Gene", eval=FALSE}
as.data.frame(E9GE_mirnagenenormal)%>%
 priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
 update_how("SERPINE2",2.75) %>%
 simulate(150) %>%
 find_iteration(limit=1, plot= TRUE) #limit=1 describes the change that is not taken into account.
```

@@

```{r, eval=FALSE}
as.data.frame(E9GE_mirnagenenormal)%>%
 priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
 update_how("SERPINE2",2.75) %>%
 simulate(100) %>%
 find_iteration(limit=1, plot= FALSE)

@@

```{r, eval=FALSE}

@@

```{r, eval=FALSE}
as.data.frame(E9GE_mirnagenenormal)%>%
  priming_graph(competing_count = GE_normal, miRNA_count = mirna_RPM, aff_factor = c(Energy, seed_type_effect), deg_factor = region_effect)%>%
  update_how("SERPINE2",2.75)%>%
  simulate(62)%>%
  as_tibble()%>%
  select(name, initial_count, count_current)->simulation_results
```

### 2.5.3 Comparison of simulation results and tumor tissue expression values
```{r, eval=FALSE}
E9GE_mirnagenetumor%>%
  dplyr::select(hgnc_symbol, GE_tumor)%>%
  dplyr::inner_join((E9GE_mirnagenenormal%>%dplyr::select(hgnc_symbol, GE_normal)), by ="hgnc_symbol")%>%
  inner_join(simulation_results, by= c("hgnc_symbol"="name"))%>%
  distinct()
```
